Characterizing Execution Times on Realistic Programs

### 2018-03-21 pt_characterization/real_data/paper.tex
Draft for 03/15

In this section we present histogram data 
for two main programs: {\it insertion sort} and {\it matrix multiplication}. 
For the runs of these programs, we varied their input sizes by 2{\small $\times$} 
and measured execution times of the programs over each input size.

\subsection{Insertion sort~\label{sec:sort}} 
This section shows a series of histograms of an insertion sort program. 
The program repeatedly runs 40 times for a given input size. 
The input size for the program 
varies from 100,000 to 3,200,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements.

Figures~\ref{fig:sort1} and ~\ref{fig:sort2} exhibit 
histograms of the execution times measured on the same insertion sort program as 
the input size grows from 100K to 800K elements by the steps of 2x. 
Note that we used one standard deviation in Figure~\ref{fig:sort400_dist} as
a couple of outliers, which were not eliminated by the original protocol, 
resulted in disturbing the rendering of a clean distribution.

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT100]{
		\includegraphics[scale=0.43]{sort100_dist.eps}
		\label{fig:sort100_dist}
	}
	\subfigure[PT frequency on SORT200]{
		\includegraphics[scale=0.43]{sort200_dist.eps}
		\label{fig:sort200_dist}
	}
	\subfigure[PT frequency on SORT400]{
		\includegraphics[scale=0.43]{sort400_dist.eps}
		\label{fig:sort400_dist}
	}
	\subfigure[PT frequency on SORT800]{
		\includegraphics[scale=0.43]{sort800_dist.eps}
		\label{fig:sort800_dist}
	}
	\caption{PT Histograms of SORT100 ... SORT800~\label{fig:sort1}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT1600]{
		\includegraphics[scale=0.43]{sort1600_dist.eps}
		\label{fig:sort1600_dist}
	}
	\subfigure[PT frequency on SORT3200]{
		\includegraphics[scale=0.43]{sort3200_dist.eps}
		\label{fig:sort3200_dist}
	}
	\caption{PT Histograms of SORT1600 and SORT3200~\label{fig:sort2}}
\end{figure}

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in column major 
as the input sizes grows from 1000x1000 to 8000x8000 by the steps of 2{\small $\times$}..

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATC1000]{
		\includegraphics[scale=0.43]{matc1000_dist.eps}
		\label{fig:matc100_dist}
	}
	\subfigure[PT frequency on MATC2000]{
		\includegraphics[scale=0.43]{matc2000_dist.eps}
		\label{fig:matc200_dist}
	}
	\subfigure[PT frequency on MATC4000]{
		\includegraphics[scale=0.43]{matc4000_dist.eps}
		\label{fig:matc400_dist}
	}
	\subfigure[PT frequency on MATC8000]{
		\includegraphics[scale=0.43]{matc8000_dist.eps}
		\label{fig:matc800_dist}
	}
	\caption{PT Histograms of MATC1000 ... MATC8000~\label{fig:matc}}
\end{figure}

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in row major 
as the input sizes grows from 1K$\times$1K to 8K$\times$8K by the steps of 2{\small $\times$}.

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATR1000]{
		\includegraphics[scale=0.43]{matr1000_dist.eps}
		\label{fig:matr100_dist}
	}
	\subfigure[PT frequency on MATR2000]{
		\includegraphics[scale=0.43]{matr2000_dist.eps}
		\label{fig:matr200_dist}
	}
	\subfigure[PT frequency on MATR4000]{
		\includegraphics[scale=0.43]{matr4000_dist.eps}
		\label{fig:matr400_dist}
	}
	\subfigure[PT frequency on MATR8000]{
		\includegraphics[scale=0.43]{matr8000_dist.eps}
		\label{fig:matr800_dist}
	}
	\caption{PT Histograms of MATR1000 ... MATR8000~\label{fig:matr}}
\end{figure}

>>>>

In this section we present histogram data 
for two main programs: {\it insertion sort} and {\it matrix multiplication}. 
For the runs of these programs, we varied their input sizes by 2{\small $\times$} while trying 
some intermediate sizes increased by $\sqrt{2}$ and measured execution times of the programs over each input size.

\subsection{Insertion sort~\label{sec:sort}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
The input size for the program 
varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements.

Figures~\ref{fig:sort1} and ~\ref{fig:sort2} exhibit 
histograms of the execution times measured on the same insertion sort program as 
the input size grows from 100K to 1,160K elements.% by the steps of 2x. 
Note that we used one standard deviation in Figure~\ref{fig:sort400_dist} as
a couple of outliers, which were not eliminated by the original protocol, 
resulted in disturbing the rendering of a clean distribution.

\begin{figure}[h]
	\centering
%	\subfigure[PT frequency on SORT25]{
%		\includegraphics[scale=0.43]{sort25_dist.eps}
%		\label{fig:sort25_dist}
%	}
%	\subfigure[PT frequency on SORT50]{
%		\includegraphics[scale=0.43]{sort50_dist.eps}
%		\label{fig:sort50_dist}
%	}
	\subfigure[PT frequency on SORT100]{
		\includegraphics[scale=0.43]{sort100_dist.eps}
		\label{fig:sort100_dist}
	}
	\subfigure[PT frequency on SORT144]{
		\includegraphics[scale=0.43]{sort144_dist.eps}
		\label{fig:sort144_dist}
	}
	\subfigure[PT frequency on SORT200]{
		\includegraphics[scale=0.43]{sort200_dist.eps}
		\label{fig:sort200_dist}
	}
	\subfigure[PT frequency on SORT288]{
		\includegraphics[scale=0.43]{sort288_dist.eps}
		\label{fig:sort288_dist}
	}
	\caption{PT Histograms of SORT25 ... SORT288~\label{fig:sort1}}
\end{figure}

\clearpage
\pagebreak

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT400]{
		\includegraphics[scale=0.43]{sort400_dist.eps}
		\label{fig:sort400_dist}
	}
	\subfigure[PT frequency on SORT580]{
		\includegraphics[scale=0.43]{sort580_dist.eps}
		\label{fig:sort588_dist}
	}
	\subfigure[PT frequency on SORT800]{
		\includegraphics[scale=0.43]{sort800_dist.eps}
		\label{fig:sort800_dist}
	}
	\subfigure[PT frequency on SORT1000]{
		\includegraphics[scale=0.43]{sort1000_dist.eps}
		\label{fig:sort1000_dist}
	}
	\caption{PT Histograms of SORT400 ... SORT1000~\label{fig:sort2}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT1160]{
		\includegraphics[scale=0.43]{sort1160_dist.eps}
		\label{fig:sort1160_dist}
	}
	\subfigure[PT frequency on SORT2320 (not complete)]{
		\includegraphics[scale=0.43]{sort2320_dist.eps}
		\label{fig:sort2320_dist}
	}
	\caption{PT Histograms of SORT1160 ... SORT2320~\label{fig:sort3}}
\end{figure}

%\begin{comment}

%\clearpage
%\pagebreak
%
%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on SORT2320 (Will be updated with the rest.)]{
%		\includegraphics[scale=0.43]{sort2320_dist.eps}
%		\label{fig:sort2320_dist}
%	}
%	\subfigure[PT frequency on SORT3200]{
%		\includegraphics[scale=0.43]{sort3200_dist.eps}
%		\label{fig:sort3200_dist}
%	}
%	\\
%	\subfigure[PT frequency on SORT4640]{
%		%\includegraphics[scale=0.43]{sort4640_dist.eps}
%		\framebox(200,200){Will be available soon.}
%		\label{fig:sort4640_dist}
%	}
%	\subfigure[PT frequency on SORT6400]{
%		\includegraphics[scale=0.43]{sort6400_dist.eps}
%		\label{fig:sort6400_dist}
%	}
%	\caption{PT Histograms of SORT2320 ... SORT6400~\label{fig:sort3}}
%\end{figure}

\clearpage
\pagebreak

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in column major 
as the input sizes grows.

%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on MATC250]{
%		\includegraphics[scale=0.43]{matc250_dist.eps}
%		\label{fig:matc250_dist}
%	}
%	\subfigure[PT frequency on MATC500]{
%		\includegraphics[scale=0.43]{matc500_dist.eps}
%		\label{fig:matc500_dist}
%	}
%	\subfigure[PT frequency on MATC1024]{
%		\includegraphics[scale=0.43]{matc1024_dist2.eps}
%		\label{fig:matc1024_dist}
%	}
%	\subfigure[PT frequency on MATC1440]{
%		\includegraphics[scale=0.43]{matc1440_dist.eps}
%		\label{fig:matc1440_dist}
%	}
%	\caption{PT Histograms of MATC250 ... MATC1440~\label{fig:matc}}
%\end{figure}
%
%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on MATC2048]{
%		\includegraphics[scale=0.43]{matc2048_dist2.eps}
%		\label{fig:matc2048_dist}
%	}
%	\subfigure[PT frequency on MATC2880]{
%		\includegraphics[scale=0.43]{matc2880_dist.eps}
%		\label{fig:matc2880_dist}
%	}	
%	\subfigure[PT frequency on MATC4096]{
%		\includegraphics[scale=0.43]{matc4096_dist2.eps}
%		\label{fig:matc4096_dist}
%	}	
%	\subfigure[PT frequency on MATC5760]{
%		\includegraphics[scale=0.43]{matc5760_dist.eps}
%		\label{fig:matc5760_dist}
%	}	
%	\caption{PT Histograms of MATC2048 ... MATC5760~\label{fig:matc2}}
%\end{figure}
%
%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on MATC8192]{
%		\includegraphics[scale=0.43]{matc8192_dist2.eps}
%		\label{fig:matc8192_dist}
%	}
%	\subfigure[PT frequency on MATC11520]{
%		\includegraphics[scale=0.43]{matc11520_dist.eps}
%		\label{fig:matc11520_dist}
%	}
%	\subfigure[PT frequency on MATC16000]{
%		\includegraphics[scale=0.43]{matc16000_dist.eps}
%		\label{fig:matc16000_dist}
%	}
%	\subfigure[PT frequency on MATC23040]{
%		\includegraphics[scale=0.43]{matc23040_dist.eps}
%		\label{fig:matc23040_dist}
%	}
%	\caption{PT Histograms of MATC8192 ... MATC23040~\label{fig:matc3}}
%\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATC1K]{
		\includegraphics[scale=0.43]{matc1024_dist.eps}
		\label{fig:matc1k_dist}
	}
	\subfigure[PT frequency on MATC2K]{
		\includegraphics[scale=0.43]{matc2048_dist.eps}
		\label{fig:matc2k_dist}
	}
	\subfigure[PT frequency on MATC4K]{
		\includegraphics[scale=0.43]{matc4096_dist.eps}
		\label{fig:matc4k_dist}
	}
	\subfigure[PT frequency on MATC8K]{
		\includegraphics[scale=0.43]{matc8192_dist.eps}
		\label{fig:matc8k_dist}
	}
	\caption{PT Histograms of MATC1024 ... MATC8192~\label{fig:matc}}
\end{figure}

\clearpage
\pagebreak

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in row major as the input sizes grows.

%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on MATR250]{
%		\includegraphics[scale=0.43]{matr250_dist.eps}
%		\label{fig:matr250_dist}
%	}
%	\subfigure[PT frequency on MATR500]{
%		\includegraphics[scale=0.43]{matr500_dist.eps}
%		\label{fig:matr500_dist}
%	}
%	\subfigure[PT frequency on MATR1024]{
%		\includegraphics[scale=0.43]{matr1024_dist2.eps}
%		\label{fig:matr1024_dist}
%	}
%	\subfigure[PT frequency on MATR1440]{
%		\includegraphics[scale=0.43]{matr1440_dist.eps}
%		\label{fig:matr1440_dist}
%	}
%	\caption{PT Histograms of MATR250 ... MATR1440~\label{fig:matr}}
%\end{figure}

%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on MATR2048]{
%		\includegraphics[scale=0.43]{matr2048_dist2.eps}
%		\label{fig:matr2048_dist}
%	}
%	\subfigure[PT frequency on MATR2880]{
%		\includegraphics[scale=0.43]{matr2880_dist.eps}
%		\label{fig:matr2880_dist}
%	}	
%	\subfigure[PT frequency on MATR4096]{
%		\includegraphics[scale=0.43]{matr4096_dist2.eps}
%		\label{fig:matr4096_dist}
%	}	
%	\subfigure[PT frequency on MATR5760]{
%		\includegraphics[scale=0.43]{matr5760_dist.eps}
%		\label{fig:matr5760_dist}
%	}	
%	\caption{PT Histograms of MATR2048 ... MATR5760~\label{fig:matr2}}
%\end{figure}
%
%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on MATR8192]{
%		\includegraphics[scale=0.43]{matr8192_dist2.eps}
%		\label{fig:matr8192_dist}
%	}
%	\subfigure[PT frequency on MATR11520]{
%		\includegraphics[scale=0.43]{matr11520_dist.eps}
%		\label{fig:matr11520_dist}
%	}	
%	\subfigure[PT frequency on MATR16000]{
%		\includegraphics[scale=0.43]{matr16000_dist.eps}
%		\label{fig:matr16000_dist}
%	}
%	\subfigure[PT frequency on MATR23040]{
%		\includegraphics[scale=0.43]{matr23040_dist.eps}
%		\label{fig:matr23040_dist}
%	}
%	\caption{PT Histograms of MATR8192 ... MATR23040~\label{fig:matr3}}
%\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATR1K]{
		\includegraphics[scale=0.43]{matr1024_dist.eps}
		\label{fig:matr1k_dist}
	}
	\subfigure[PT frequency on MATR2K]{
		\includegraphics[scale=0.43]{matr2048_dist.eps}
		\label{fig:matr2k_dist}
	}
	\subfigure[PT frequency on MATR4K]{
		\includegraphics[scale=0.43]{matr4096_dist.eps}
		\label{fig:matr4k_dist}
	}
	\subfigure[PT frequency on MATR8K]{
		\includegraphics[scale=0.43]{matr8192_dist.eps}
		\label{fig:matr8k_dist}
	}
	\caption{PT Histograms of MATR1K ... MATR8K~\label{fig:matr}}
\end{figure}

\clearpage
\pagebreak

%\end{comment}
